Query Optimization for Dynamic Imputation

### 2017-05-12 rebuttal.tex

  \section{Reviewer 2}
  \begin{itemize}
  \item 1) No new imputation method is presented. The model relies on external imputation techniques, and given it's done on-the-fly, presumably imputed values depend on qualifying query records.

    \resp{Our contribution is the planning algorithm which allows imputation to be interleaved into the query plan.
      We do not present a new imputation method, but our technique is agnostic to the particular imputation method used.
      We reduce the overhead of imputation by performing it only on the tuples which are relevant to a particular query, so the imputed results do depend on the records which are relevant to particular query.}

  \item 2) No comparative evaluation against existing imputation/data cleaning techniques.

    \resp{
      We compare our planning technique for on-the-fly imputation to imputation performed on the full dataset, using the same imputation algorithm in both cases.
      We are not aware of another database technology which offers on-the-fly imputation optimization, so there is no direct comparison for the planning algorithm.
      However, we ran a simple experiment using BayesDB to compare possible imputation times. In order to make the comparison as fair as possible in terms of running
      time, we reduced the number of models that BayesDB instantiates to a single model per base table. We fit each model with 100 iterations, in an optimized setting.
      The fitting times on the CDC tables ranged between 119 and 320 seconds (per table). The FCC model fitting took 237 seconds. The user would then still need to use these models to
      perform imputation.  The underlying modeling technique for BayesDB is quite sophisticated, so the high running time is not a surprise, but should provide some context
      for the challenges faced by users trying to explore new datasets. In a real world scenario, the user would instantiate more than a single model, increasing these running
      times further.
      % Our evaluation compares our technique to an imputation of the full dataset. We use the same imputation algorithm for our on-the-fly imputation as for the full dataset imputation. Cleaning the full dataset is the standard method of handling missing values.
    }

### 2017-05-14 paper/experiments.tex
Move some text inside captions

\begin{figure}
\includegraphics[width=\columnwidth]{figures/running_times_combined_bar.png}
\caption{Runtimes for the queries in~\Cref{tbl:queries}. $\alpha=0$ (resp. $\alpha=1$) is \ProjectName{} run at the highest (resp. lowest) quality setting. Baseline is full table imputation followed by running the query.}
\todo{update with new figure}   
\label{fig:runtimes}
\end{figure}

@@

All experiments were run on a single Amazon Web Services EC2 {\tt c4.xlarge} instance, with
four 2.9 GHz Intel Xeon E5--2666 v3 virtual CPUs and 7.5 GiB of main memory, on Debian Linux.
Each query and each value of $\alpha$ was run 200 times, after discarding a warm-up period.

@@

In our case, the relevant comparison is against traditional imputation on the base table, given the unavailability of ground truth.

@@

Queries optimized
    for quality ($\alpha=0$) generally achieve lower error than queries optimized for
    efficiency ($\alpha=1$). The count fraction column shows the number of tuples used in calculating each aggregate
     as a fraction of the number of tuples used when running the same query after imputing on the base table.
    A lower count share reflects more potential for errors.

\begin{table}
\centering
\input{tables/perf_summary.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$ parameterizations, as compared to the baseline.}
\todo{update with new figure}
\label{table:smape}
\end{table}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{figures/running_times_combined_bar.png}
\caption{Runtimes for the queries in~\Cref{tbl:queries} using reference
    chained-equation decision trees algorithm. $\alpha=0$ (resp. $\alpha=1$) is
    \ProjectName{} run at the highest (resp. lowest) quality setting. Baseline
    is full table imputation followed by running the query. Each query and each
    value of $\alpha$ was run 200 times.}
\todo{update with new figure}   
\label{fig:runtimes}
\end{figure}

@@

@@

@@

\begin{table}
\centering
\input{tables/perf_summary.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$ parameterizations, as compared to the baseline.
Queries optimized
    for quality ($\alpha=0$) generally achieve lower error than queries optimized for
    efficiency ($\alpha=1$). The count fraction column shows the number of tuples used in calculating each aggregate
     as a fraction of the number of tuples used when running the same query after imputing on the base table.
    A lower count share reflects more potential for errors.}
\todo{update with new figure}
\label{table:smape}
\end{table}
